Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-17 Manuscript/00-main.Rmd
Add real data graphs to the manuscript

tar_load(WLM_train_dat)
# tar_load(tbl_one)
tar_load(ECB_bamlasso_cv)
tar_load(ECB_SBGAM_cv)
tar_load(WLM_bamlasso_cv)
tar_load(WLM_SBGAM_cv)
tar_load(tbl_real_time)
# tar_load(sim_tim_tab)
```

@@

>>>>

tar_load(WLM_train_dat)
# tar_load(tbl_one)
tar_load(ECB_bamlasso_cv)
tar_load(ECB_SBGAM_cv)
tar_load(WLM_bamlasso_cv)
tar_load(WLM_SBGAM_cv)
tar_load(tbl_real_time)
tar_load(ECB_plot)
tar_load(WLM_plot)
# tar_load(sim_tim_tab)
```

@@

\clearpage
\begin{figure}[h]
\includegraphics{Figs/ECB_plot}
\end{figure}

\begin{figure}[h]
\includegraphics{Figs/WLM_plot}
\end{figure}
